Component response rate variation underlies the stability of complex systems (revision notes)

### 2020-01-22 notebook/revision_notes.Rmd
Working through stuff again

Variation in $\gamma$ increases the total variation such that for $\textbf{M} = \gamma \textbf{A}$, $\sigma^{2}_{M_{ij}} = \sigma^{2}_{A_{ij}} \left(1 + \sigma^{2}_{\gamma_{i}} \right)$. Eigenvalues of $\textbf{A}$ are therefore enclosed within a circle centred at $d$ with a radius of $\sigma_{A_{ij}}\sqrt{SC} = \sqrt{SC\sigma^{2}_{A_{ij}}}$, while eigenvalues of $\textbf{M}$ have a larger radius of $\sqrt{SC \sigma^{2}_{A_{ij}} \left(1 + \sigma^{2}_{\gamma_{i}}\right)}$ (see blue versus red points below).

>>>>

Variation in $\gamma$ ($\sigma^{2}_{\gamma}$) **can increase or decrease the radius of the circle**.

<!--- still wrong below -- no simple analytical solution seems possible --->

$$2 \sigma_{\gamma} \sigma_{\textbf{A}} \sqrt{SC}.$$

The figure below shows the relationship between $\sigma_{\gamma}$ and the radius of the circle in which eigenvalue spectra are contained given $S = 1024$, $C = 1$, and $\sigma_{\textbf{A}} = 1/\sqrt{S}$. Values of $\gamma$ were drawn from a uniform distribution $\gamma \sim \mathcal{U}(0, b)$ at increasing values of $b$ so that $\sigma_{\gamma} = (1/12)b^2$ gradually increased.

For poisson, it's $$\sigma^{2}_{\gamma} \sigma_{\textbf{A}} \sqrt{SC}.$$

The mean of a uniform is $(1/2)b$, while the mean of the Poisson is $\lambda = \sigma^{2}_{\gamma}$

Note that the error around the expected radius of eigenvalues is not normally distributed. It is log distributed (check).
